Inefficient Concessions and Mediation

### 2023-08-09 draft_narrow.tex
highlight contribution of concessions that don't need credible commitment

In our model, concessions may act as signals or as an end in themselves -- or as both simultaneously. One contribution of this paper is that it allows concessions to have future material value, signaling value, and both. We will show that when concessions have both signaling and future material value, some of the material value of the concessions may be purposefully destroyed and thus inefficiencies can emerge.

>>>>

In our model, concessions may act as signals or as an end in themselves -- or as both simultaneously. One contribution of this paper is that it allows concessions to have future material value, signaling value, and both. We will show that when concessions have both signaling and future material value, some of the material value of the concessions may be purposefully destroyed and thus inefficiencies can emerge. Another contribution is that the way we model concessions does not require countries to make an agreement that requires credible commitment, as is common in bargaining models. Instead, countries willingly provide a concession if they expect the signal it sends to provide a benefit in terms of future cooperation and public good provision.\footnote{When mediation is required to achieve peace in the model, it relies upon a manipulative mediator to enforce the required level of concessions.}
